SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-09-18 scipy-1.0/paper.tex
MAINT: move CI definition
* expand the Figure 2 caption to direct the reader to
explanations for CI and other technical terms to address
reviewer comment that CI was not explained at this point
of manuscript

\begin{figure}[H]
\centering
\includegraphics[width=0.95\textwidth]{static/scipy_timeline}
\caption{Major milestones from SciPy's initial release in 2001 to
the release of SciPy 1.0 in 2017.}
\label{fig:timeline}
\end{figure}

>>>>

\begin{figure}[H]
\centering
\includegraphics[width=0.95\textwidth]{static/scipy_timeline}
\caption{Major milestones from SciPy's initial release in 2001 to
the release of SciPy 1.0 in 2017. Note that SciKits and GitHub 
have been introduced in the ``Background'' section;  more 
information about Cython and SciPy subpackages (e.g. 
\texttt{scipy.sparse}) is available in ``Architecture 
and implementation choices'', BLAS/LAPACK support is 
detailed in ``Key technical improvements'', and continuous
integration is discussed in ``Test and benchmark suite''.}
\label{fig:timeline}
\end{figure}
